\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-13 paper.tex
new fig

\section{Motivating example---Minimal-Time Double Integrator}

@@

\subsection{Informed set}
Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.

For the case of a double integrator, this is not the case. Intuitively, one can see why. According the the double-integrator minimum time model, maximum acceleration is applied in one direction to a point, and then maximum acceleration in the other direction is applied to complete the motion. The direction of the first and second acceleration depends on the start and goal state.

>>>>

\section{Motivating example---Minimal-Time Double Integrator (MTDI)}

@@

\subsection{Informed set}
Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.

For the case of a MTDI, this is not the case. 
Specifically, we have that 
(i)~the structure of~\Cinf changes not only with~$\hat{c}$ but also according to the specific values of the start~$x_s$ and goal~$x_g$ states
and that
(ii)~the cost map that implicitly defines~\Cinf can contain discontinuities (in contrast to Euclidean spaces minimizing path length where the cost map is continuous and differentiable at every point).

To understand the differences recall that optimal paths for MTDI follows a ``bang-bang`` controller. Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
It is straightforward to see that both the type and the amount of acceleration applied (and hence the structure of~\Cinf) depend on the specific values of~$x_s$ and~$x_g$. 
Fig~\ref{fig:informed_sets} 
depicts two informed sets defined using the same cost~$\hat{c}$ using different start and goal states. Notice the difference in structure of~\Cinf.

To understand why the cost map may not be continuous consider the simple example in Fig~\ref{fig:discont}

First, the informed

Intuitively, one can see why. According the the double-integrator minimum time model, maximum acceleration is applied in one direction to a point, and then maximum acceleration in the other direction is applied to complete the motion. The direction of the first and second acceleration depends on the start and goal state.
